Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2018-06-22 WholePlotTrajectories.tex
Update WholePlotTrajectories.tex

\Abstract{
Understand the maintenance of forests biodiversity structure,
functioning and dynamics is urgent to anticipate their fate in the
global changing context. Communities diversity are assumed to be shaped
by constant regime of disturbance yielding a diversity peak at
intermediate intensity, but for tropical forests this intermediate
disturbance hypothesis (IDH) remains debated as well as the completeness
their resilience in all taxonomic and functional facets after
disturbance. To disentangle the ecological processes driving communities
response to disturbance we analysed the taxonomic and functional
trajectories following a logging and thinning disturbance gradient.
Specifically we examined over 30 years the trajectories of communities
taxonomic richness and evennes and functional composition, diversity and
redundancy based on 7 leaf, stem and life history traits assessing
species ecology. Trajectories highlighted communities taxonomic
resilience, maintaining their initial differences in composition, and
functional resilience through fast functional trajectory common to all
communities in the functional space. The IDH consistently predicted
communities functional trajectories according to the disturbance
intensity, but poorly represented their taxonomic trajectories, blurried
by the alteration of the functional redundancy and the recruitment of
infrequent, shade tolerant species slowed by competitive exclusion
processes. Although communities functioning had recovered after 30 years
their taxonomic diversity and composition in infrequent species and
their functional redundancy remained altered. these results acknowledged
the need of decades-long recovery cycles to ensure communities complete
resilience, and questioned communities maintenance after repeated
disturbance.
}

>>>>

\Abstract{
Understanding the ecological rules underlying the maintenance of tropical forest biodiversity, structure,
functioning and dynamics is urgent to anticipate their fate in the
global changing context. Communities diversity are assumed to be shaped
by constant regime of disturbance yielding a diversity peak at
intermediate intensity, but for tropical forests this intermediate
disturbance hypothesis (IDH) remains debated as well as the completeness
their resilience in all taxonomic and functional facets after
disturbance. To disentangle the ecological processes driving communities
response to disturbance we analysed the taxonomic and functional
trajectories following a logging and thinning disturbance gradient.
Specifically we examined over 30 years the trajectories of communities
taxonomic richness and evennes and functional composition, diversity and
redundancy based on 7 leaf, stem and life history traits assessing
species ecology. Trajectories highlighted communities taxonomic
resilience, maintaining their initial differences in composition, and
functional resilience through fast functional trajectory common to all
communities in the functional space. The IDH consistently predicted
communities functional trajectories according to the disturbance
intensity, but poorly represented their taxonomic trajectories, blurried
by the alteration of the functional redundancy and the recruitment of
infrequent, shade tolerant species slowed by competitive exclusion
processes. Although communities functioning had recovered after 30 years
their taxonomic diversity and composition in infrequent species and
their functional redundancy remained altered. these results acknowledged
the need of decades-long recovery cycles to ensure communities complete
resilience, and questioned communities maintenance after repeated
disturbance.
}
